Distributed systems are notoriously complicated to build. ZooKeeper has become popular largely due
to its use as a building block to make other distributed systems less complicated. Developers rely
on ZooKeeper's strong write consistency and high read availibility to offload design complexity and
make their own systems simpler. For example, FaRM [4] uses ZooKeeper to manage configuration so that the
authors can focus on high performance design and make rare, hairy failure recovery simple. FaRM
avoids using ZooKeeper in the critical path, presumably because of ZooKeeper's relatively high
latency. Apache Kafka [5], a real-time stream processing platform, uses ZooKeeper to manage cluster
membership, leadership, and various other metadata. As with FaRM, Kafka avoids using ZooKeeper in
the system's critical path.

Despite ZooKeeper's common usage and many benchmarks reporting its average case latency [6], there
do not seem to be any reports of the system's tail latency under load. Tail latency is amongst the
most important performance characteristics in many real-world systems because these systems are
composed of many interdependent components. With high "fan out", even rare spikes in latency amongst
a small number of components can cause the overall system to respond slowly on average.  Accurate
characterization of ZooKeeper's worst case latency is important for potential application developers
to determine how best to fit ZooKeeper into high fan-out systems.

Certain aspects of ZooKeeper's design could lead to occassionaly high request latency. Some members
of the community have suggested that latency is primarily determined by the time spent spent by
followers fetching data from the leader [7]. This characteristic suggests that ZooKeeper could
potential have lower latency with a leaderless design.

In order to compare ZooKeeper to a low latency baseline, we implemented a system called Safari.
Safari aims to provide the same consistency guarantees as ZooKeeper with lower tail latency, while
sacrificing read and write throughput, availability during network partitions, and features. Our
system is currently incomplete and does not provide linearizability as intended, but serves as an
optimistic lower bound on latency that could be achieved for any system with ZooKeeper's API and
consistency.
